\textcolor{black}{Disambiguating Monocular Depth Estimation with a Single Transient: Supplemental Information}

### 2020-07-15 paper/eccv2020CR/sections/hardware.tex
Fixed Gordon's name, misc supp. changes.

\begin{figure}[t]
	\centering
  \includegraphics[width=0.8\columnwidth]{hardware.pdf}
  \caption{(a) Prototype scanning setup. The pulsed light from the laser travels
    through a beam splitter before being guided by the galvo to the scene.
    Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB 
    camera is used to capture the image used to generate the monocular depth estimate
    (the depth bccamera is not used). (b) Scene and (c) measurements for diffused and summed scanned mode. The observed
    counts in the diffuse mode match closely with the sum of the raster-scanned
    measurements.}
  \label{fig:hardware}
  % \vspace{-0.5em}
\end{figure}

>>>>

\begin{figure}[t]
	\centering
  \includegraphics[width=0.8\columnwidth]{hardware.pdf}
  \caption{(a) Prototype scanning setup. The pulsed light from the laser travels
    through a beam splitter before being guided by the galvo to the scene.
    Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB
    camera is used to capture the image used to generate the monocular depth
    estimate (the depth camera is not used). (b) Scene and (c) measurements for
    diffused and summed scanned mode (10s capture, aligned peaks). The observed
    counts in the diffuse mode match closely with the sum of the raster-scanned
    measurements.}
  \label{fig:hardware}
\end{figure}

### 2020-07-15 paper/eccv2020CR/supplement.tex
Fixed Gordon's name, misc supp. changes.

% INITIAL SUBMISSION 
%\begin{comment}
\titlerunning{ECCV-20 submission ID \ECCVSubNumber} 
\authorrunning{ECCV-20 submission ID \ECCVSubNumber} 
\author{Anonymous ECCV submission}
\institute{Paper ID \ECCVSubNumber}
%\end{comment}
%******************

% CAMERA READY SUBMISSION
\begin{comment}
\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
\end{comment}
%******************
\maketitle
\begin{abstract}
  TODO: Abstract
\end{abstract}

@@

% show this in supplement
%To verify that our digitally aggregated scanned SPAD measurements match measurements produced by an optically diffused SPAD, we set up a slightly modified version of our prototype consisting of both scanned and diffused SPADs side-by-side. Details about this system can be found in the supplement. We then captured measurements of the simple scene shown in Figure~\ref{fig:hardware}(b) with both SPADs. The aggregated measurements from the scanned SPAD are shown alongside the optically diffused SPAD's measurements in Figure ~\ref{fig:hardware}(c). These results demonstrate that the two systems produce near equivalent measurements. Slight differences in their two histograms can be attributed to a baseline difference of about 10cm between the SPAD positions. That is, they observe scene from slightly different perspectives.
	%NOTE:JUSTIFY USE OF DIFFERENT PROTOTYPE FOR RESULTS IN THE WILD WITH EYE SAFETY?} \edit{We show proof-of-concept results captured by this system in   Figure~\ref{fig:captured_diffuse_small}. For}

In order to verify that digital summation of scanned measurements yields results
that are similar to those captured by a diffused laser and detector, we capture
an example scene using a modified hardware prototype in both scanned and
diffused modes. This hardware prototype (shown in Fig.~\ref{fig:hardware}) is less mobile than 
our unmodified prototype, but allows us to use a more powerful laser (Katana
05HP, 532 nm) operated at approximately 25 mW average power. We also use two
single-pixel SPAD detectors, where one SPAD is aligned with the optical path of
the laser, and the other SPAD is operated without a lens to integrate light
from the entire scene. Both SPADs are fitted with a 10 nm bandpass filter
centered at 532 nm, which reduces the amount of integrated ambient light. We
attach a holographic diffuser (Thorlabs ED1-S50) to the laser output in order
to diffuse light onto the scene. Alternatively, we remove the diffuser and use a
pair of scanning mirrors to scan the scene.

The modified hardware setup is used to capture an example scene in both scanned and
diffused modes, and the resulting transients are used to refine an initial depth
estimate from the Kinect RGB image. We illustrate the results of this procedure
in Fig.~\ref{fig:comparison}. The reconstructions from the scanned and diffused
measurements are similar in reconstruction quality and also show similar
quantitative improvement in terms of error over the initial depth estimate. The
unnormalized photon counts are also shown in Fig.~\ref{fig:comparison}, and we
note that the counts show similar trends. The number of recorded photons in
these experiments is shown in Table~\ref{tab:photon_counts}. In both cases, the
rate of detected photons is far less ($<$5\%) than the number of emitted laser
pulses, and so we conclude that the measurements are captured in the low-flux
regime where pileup effects are negligible. We attribute most of the differences
between the scanned and diffused transients to the approximately 16 cm vertical
baseline between the positions of the diffused and scanned SPADs (see
Fig.~\ref{fig:hardware}).
\begin{figure}[H]
  \centering \includegraphics[width=\textwidth]{diffused_hardware/setup.pdf}
  \caption{Modified hardware setup. The setup is used to compare scanned and
  diffused measurements and employs two SPAD detectors and two laser
  configurations. In the first configuration, the scene is illuminated by
  sending the laser light through a holographic diffuser and a lensless SPAD 
  integrates light from the entire scene. In the second, the SPAD is aligned
  with the optical path of the laser and the scene is scanned using a pair of
  scanning mirrors. The baseline between the two SPADs (right) results in some
  observed differences in the recorded transients.}
  \label{fig:hardware}
\end{figure}

\begin{figure}[H]
  \centering \includegraphics[width=\textwidth]{captured_diffuse.pdf}
  \caption{Comparison of scan + sum and diffused SPAD. The transients are captured
      with the same total exposure time and are qualitatively similar without 
      noticeable pileup effects. We Use $K = 300$ bins for the reconstruction
      and a depth range of $[0.8, 6]$ meters. MiDaS \cite{Lasinger:2019} does
      not produce globally-scaled depth, so we scale it to fit this depth range.
      We inpaint the depth map from the Kinect's depth camera to acquire ground
      truth depth.}
  \label{fig:comparison}
\end{figure}

>>>>

% INITIAL SUBMISSION 
%\begin{comment}
% \titlerunning{ECCV-20 submission ID \ECCVSubNumber}
% \authorrunning{ECCV-20 submission ID \ECCVSubNumber}
% \author{Anonymous ECCV submission}
% \institute{Paper ID \ECCVSubNumber}
%\end{comment}
%******************

% CAMERA READY SUBMISSION
% \begin{comment}
\titlerunning{Disambiguating Monocular Depth Estimation with a Single Transient}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mark Nishimura  \and
David B. Lindell \and
Christopher A. Metzler \and \\
Gordon Wetzstein}

%
\authorrunning{M. Nishimura et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Stanford University, Stanford, CA \\
\email{\{markn1, lindell, cmetzler, gordon.wetzstein\}@stanford.edu}}
% \end{comment}
%******************
\maketitle
% \begin{abstract}
%   TODO: Abstract
% \end{abstract}

@@

%To verify that our digitally aggregated scanned SPAD measurements match measurements produced by an optically diffused SPAD, we set up a slightly modified version of our prototype consisting of both scanned and diffused SPADs side-by-side. Details about this system can be found in the supplement. We then captured measurements of the simple scene shown in Figure~\ref{fig:hardware}(b) with both SPADs. The aggregated measurements from the scanned SPAD are shown alongside the optically diffused SPAD's measurements in Figure ~\ref{fig:hardware}(c). These results demonstrate that the two systems produce near equivalent measurements. Slight differences in their two histograms can be attributed to a baseline difference of about 10cm between the SPAD positions. That is, they observe scene from slightly different perspectives.
	%NOTE:JUSTIFY USE OF DIFFERENT PROTOTYPE FOR RESULTS IN THE WILD WITH EYE SAFETY?} \edit{We show proof-of-concept results captured by this system in   Figure~\ref{fig:captured_diffuse_small}. For}

In order to verify that digital summation of scanned measurements yields results
that are similar to those captured by a diffused laser and detector, we capture
an example scene using a modified hardware prototype in both scanned and
diffused modes. This hardware prototype (shown in Fig.~\ref{fig:hardware}) is less mobile than 
our unmodified prototype (which was able capture a wider variety of scenes,
including outdoors, along with their ground truth
depths), but allows us to use a more powerful laser (Katana 05HP, 532 nm)
operated at approximately 25 mW average power. We also use two single-pixel SPAD
detectors, where one SPAD is aligned with the optical path of the laser, and the
other SPAD is operated without a lens to integrate light from the entire scene.
Both SPADs are fitted with a 10 nm bandpass filter centered at 532 nm, which
reduces the amount of integrated ambient light. We attach a holographic diffuser
(Thorlabs ED1-S50) to the laser output in order to diffuse light onto the scene.
Alternatively, we remove the diffuser and use a pair of scanning mirrors to scan
the scene.

The modified hardware setup is used to capture an example scene in both scanned and
diffused modes, and the resulting transients are used to refine an initial depth
estimate from the Kinect RGB image. We illustrate the results of this procedure
in Fig.~\ref{fig:comparison}. The reconstructions from the scanned and diffused
measurements are similar in reconstruction quality and also show similar
quantitative improvement in terms of error over the initial depth estimate. The
unnormalized photon counts are also shown in Fig.~\ref{fig:comparison}, and we
note that the counts show similar trends. The number of recorded photons in
these experiments is shown in Table~\ref{tab:photon_counts}. In both cases, the
rate of detected photons is far less ($<$5\%) than the number of emitted laser
pulses, and so we conclude that the measurements are captured in the low-flux
regime where pileup effects are negligible. We attribute most of the differences
between the scanned and diffused transients to the approximately 16 cm vertical
baseline between the positions of the diffused and scanned SPADs (see
Fig.~\ref{fig:hardware}).
\begin{figure}[ht!]
  \centering \includegraphics[width=0.8\textwidth]{diffused_hardware/setup.pdf}
  \caption{Modified hardware setup. The setup is used to compare scanned and
  diffused measurements and employs two SPAD detectors and two laser
  configurations. In the first configuration, the scene is illuminated by
  sending the laser light through a holographic diffuser and a lensless SPAD 
  integrates light from the entire scene. In the second, the SPAD is aligned
  with the optical path of the laser and the scene is scanned using a pair of
  scanning mirrors. The baseline between the two SPADs (right) results in some
  observed differences in the recorded transients.}
  \label{fig:hardware}
\end{figure}

\begin{figure}[ht!]
  \centering \includegraphics[width=\textwidth]{captured_diffuse.pdf}
  \caption{Comparison of scan + sum and diffused SPAD. The transients are captured
      with the same total exposure time and are qualitatively similar without 
      noticeable pileup effects. We use $K = 300$ bins for the reconstruction
      and a depth range of $[0.8, 6]$ meters. MiDaS \cite{Lasinger:2019} does
      not produce globally-scaled depth, so we scale it to fit this depth range.
      We inpaint the depth map from the Kinect's depth camera to acquire ground
      truth depth.}
  \label{fig:comparison}
\end{figure}
